---
title: "ms_3.Rmd"
author: "Richard Zhu"
date: "2/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r Loading in Data, include = FALSE}
library(tidyverse)
library(rvest)
library(janitor)
# Read in csv files from Kaggle - Oscar winners by demographics and information about the Oscar Winners
demographics <- read_csv("raw-data/Oscars-demographics-DFE.csv") %>%
  clean_names()
oscars_overall <- read_csv("raw-data/the_oscar_award.csv") %>%
  clean_names() %>%
  select(year_ceremony, category, name, film, winner) %>%
  setNames(c("year", "category", "name", "film", "winner"))

```


```{r Cannes Data, include = FALSE}
# Use rvest package to scrape data from Wikipedia from Cannes Film Festival
# Cannes Data - Palme D'Or
cannes_html <- read_html("https://en.wikipedia.org/wiki/Palme_d%27Or") %>%
  html_nodes("table")
palme_dor <- cannes_html[[2]] %>%
  html_table(fill=TRUE) %>%
  clean_names()
```


```{r BAFTA Data, include = FALSE}
# BAFTA Data - Best International Feature Film
bafta_tables <- read_html("https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Film_Not_in_the_English_Language") %>%
  html_nodes("table")

bafta_1980s <- bafta_tables[[2]] %>% html_table()
bafta_1990s <- bafta_tables[[3]] %>% html_table()
bafta_2000s <- bafta_tables[[4]] %>% html_table()
bafta_2010s <- bafta_tables[[5]] %>% html_table(fill=TRUE)
colnames(bafta_2010s) <- c("Film", "Director(s)", "Producer(s)", "Country", "trash1", "trash2")
bafta_2010s <- bafta_2010s %>%
  select(1:4)

  
# compiled bafta data
bafta <- do.call("rbind", list(bafta_1980s, bafta_1990s, 
                             bafta_2000s, bafta_2010s))
colnames(bafta) <- c("film", "director", "producer", "country")
```


```{r Oscars Data, include = FALSE}
# Oscars BIFF
# Overall statistics for BIFF countries, submissions, nominations
oscars_biff_overall <- read_html("https://en.wikipedia.org/wiki/List_of_countries_by_number_of_Academy_Awards_for_Best_International_Feature_Film") %>%
  html_nodes("table")

# Function to take out &&& and + from the biff_countries entries
replace_and <- function(s) {
  as.numeric(str_replace_all(s, "[^[:alnum:]]", ""))
}

biff_countries <- oscars_biff_overall[[1]] %>% 
  html_table() %>%
  setNames(c("country", "winners", "nominations", "submissions")) %>%
  mutate(winners = replace_and(winners),
         nominations = replace_and(nominations),
         submissions = replace_and(submissions))

biff_year <- oscars_biff_overall[[2]] %>% html_table() %>%
  setNames(c("year", "ceremony", "submissions", "first_time")) %>%
  select(year, submissions, first_time)

```



## International or Local Films?: The Oscars by Country and Demographic Over Time
In 2019, Bong Joon Ho, the South Korean director of recent Best Picture winner Parasite, said in an interview that “the Oscars are not an international film festival. They’re very local.” Of course, soon after his interivew, Parasite took the Oscars by storm with 6 nominations and 4 eventual wins, dominating the February award show with wins in major categories of Best Picture, Best Director, Best International Feature, and Best Original Screenplay. 

Parasite was the first non-English movie to win the Best Picture honor, symbolic of the Oscars' recent shift towards more internationalism and diversity. Indeed, historically the Oscars have had a reputation of being monolithic and focusing on the stories of a select few Americans. Bong's reference to the Oscars as "local" was preceded by the #OscarsSoWhite movement that spotlighted the lack of minority representation in Oscar nominations and membership. Correspondingly, I believe that it would be interesting to analyze the demographics and geography of the Oscars' awards over time, to see if there was a broader context of diversification that accompanied Parasite's historic win.

## Data
When Bong spoke about the Oscars being local, he later contextualized that he was comparing the Oscars to other famous international film festivals such as the Cannes Film Festival and Venice Film Festival. As a result, I wanted to compare the Oscars' awards of Best International Feature Film with the equivalent of Best Picture at Cannes - the Palme d'Or. Additionally, I compared the BIFF award at the Oscars with its equivalent at the BAFTAs - the British film academy.

Moreover, I wanted to see how different nations progressed in their film industries over time through investigating the amount of submissions and nominations for International Feature Film. As a result, I also looked into the winners, nominations, and submissions of each country for the Oscars' BIFF category from web scraping on Wikipedia. I wanted to make a visual representation of film's development all around the world, and looking at these datasets allowed me to do so.

Finally, I wanted to look into the demographics of the Oscars' nominations and winners over time. Regressing the Oscars membership with its eventual results provides interesting insights into whether the representation within membership necessarily causes more diverse winners and nominees. Thus, I utilized online data from Kaggle to download demographic information of Oscars nominees historically to see the progress of representation over time.

## About Me
Hello! My name is Richard Zhu, and I'm a sophomore in Leverett House studying Applied Math with a focus in Economics and Computer Science. This is was my final project for GOV 1005: Data. If you're interested in contacting me, my email is richardzhu\@college.harvard.edu